---
title: "Population identification with microarray signatures matching"
output:
  html_document:
    df_print: paged
---

In this script, we load the population signatures defined using our microarrays experiments
We then select the top genes for each signature, and calculate a UCell score for each signature in each cell.
Cells are individually attributed to populations based on the highest score amongst signatures.

Libraries
```{r Libraries}
library(tidyverse)
library(dplyr)
library(patchwork)
library(Seurat, lib.loc = "/opt/rstudio-server_conda/conda/envs/rstudio-server_4.1.0/lib/R/library/")
library(readr)
library(UCell)
library(ggplot2)
library(circlize)
library(scales)
library(openxlsx)
```

Loading required objects
This analysis is focused on NPC populations, therefore we will use a subset of the base object
```{r Import objects}
SCT_obj <- readRDS("Objects/SCT_obj.rds")
Biomart_annotated <- read.csv("Analysis_tools/Biomart_annotated.csv")
geneIDs <- # For easy calling of genes through external gene name
  Biomart_annotated[!duplicated(Biomart_annotated$external_gene_name),1]
names(geneIDs) <- Biomart_annotated[!duplicated(Biomart_annotated$external_gene_name),2]
```

Distinction of astrocytes and qNSC using UCell Score

Loading genesets from Cebrian-Silla et al. 2021, selecting Top 100 genes

```{r Import signatures astro-qNSC}
Astrocytes_markers <- read.xlsx("All_inputs/Cebrian-Silla/elife_67436_supp1_v3.xlsx", sheet = 1)
B_cells_markers <- read.xlsx("All_inputs/Cebrian-Silla/elife_67436_supp1_v3.xlsx", sheet = 3)
Astro_vs_B <- list(geneIDs[Astrocytes_markers$genes][1:100], geneIDs[B_cells_markers$genes][1:100])
names(Astro_vs_B) <- c("Astrocytes", "B_Cells")
```

Selecting astrocytes and B cells
```{r Selecting astrocytes and B cells}
clusters_of_Astro <- c("4", "13")

Astro_obj <- subset(SCT_obj, clusters %in% clusters_of_Astro)
```

Running UCell
```{r Running UCell}
DefaultAssay(Astro_obj) <- "SCT" # Run on normalized counts
method_UC <- "_UC_Score"
Astro_obj <-
  AddModuleScore_UCell(
    obj = Astro_obj,
    features = Astro_vs_B,
    name =  method_UC,  
    assay = "SCT"
  )#suffix for metadata
```

Creating new metadata column containing the name of the highest score
```{r Metadata creation}
Astro_obj$Astro_vs_B <- 
  colnames(Astro_obj@meta.data[,
                             paste0(names(Astro_vs_B), method_UC)])[
                     apply(Astro_obj@meta.data[,
                                             paste0(names(Astro_vs_B),
                                                    method_UC)], 
                           1,
                           function(vec) {which(vec == max(vec))})
                     ]
```

Metadata addition
```{r Metadata addition}
SCT_obj <- AddMetaData(SCT_obj, 
                       metadata = Astro_obj$Astro_vs_B, 
                       col.name = "Astro_vs_B")
UMAPPlot(SCT_obj, group.by = "Astro_vs_B", label = T) + NoLegend()
```


Loading population signatures from bulk transcriptome data (Supp. Material #) 
```{r Loading populations}
names_sig <- c("qNSC", "aNSC", "TAP", "iNB", "mNB")

Population_signatures <- lapply(X = paste0("All_inputs/Microarray_signatures/", 
                                           names_sig,
                                           "_signature.xlsx"),
                                FUN = read.xlsx)
```

Selection of genes present in SCT assay and determination of top 100 highest fold-change
```{r Top100 genes}
Population_signatures <- 
  lapply(X = 1:length(names_sig),
         FUN = function(signature_nb){
           signature_list <- merge(x = Population_signatures[[signature_nb]],
                                   y = Biomart_annotated,
                                   by.x = "gene",
                                   by.y = "external_gene_name",
                                   all.x = TRUE) %>%
             filter(!is.na(description)) %>% # Use subset and select
             arrange(desc(FC))
           signature_list$...1 <- NULL
           signature_list$Population <- names_sig[[signature_nb]]
           signature_list <- 
             filter(signature_list, ensembl_gene_id %in%
                      rownames(SCT_obj@assays[["SCT"]]@data)) %>%
             arrange(desc(FC))
           write.csv(signature_list[1:100,], row.names = FALSE,
                     file = paste0("Outputs/Population_signatures_top100/Top100_", 
                                   names_sig[[signature_nb]], 
                                   "_signature.csv")) #Returns the provided gene lists
           return(signature_list[1:100,"ensembl_gene_id"])
         })

names_sig2 <- paste0("s_", names_sig)
names(Population_signatures) <- names_sig2
```

Calculation of UCell Score for each signature (s-TAP has only 99 genes, producing a NA warning for position 100)
```{r UCell score NPC}
NPC_obj <- subset(SCT_obj, NPC == "NPC") 

DefaultAssay(NPC_obj) <- "SCT"

NPC_obj <-
  AddModuleScore_UCell(
    obj = NPC_obj,
    features = Population_signatures,
    name = method_UC,
    assay = "SCT",
    slot = "counts")
```

Retrieve UCell scores and ID from object, then assign cell to population based on highest score
```{r Assign population identity}
NPC_obj$Identity <-  
  colnames(NPC_obj@meta.data[,
                             paste0(names_sig2, method_UC)])[
                               apply(NPC_obj@meta.data[,
                                                       paste0(names_sig2,
                                                              method_UC)],
                                     1,
                                     function(vec) {which(vec == max(vec))})
                               ]


Identity_convert <- paste0("s-", names_sig)
names(Identity_convert) <- paste0(names_sig2, method_UC)

Idents(NPC_obj) <- "Identity"
NPC_obj <- RenameIdents(NPC_obj, Identity_convert)

NPC_obj$Identity <- Idents(NPC_obj)
NPC_obj$Identity <- factor(Idents(NPC_obj), levels = Identity_convert)

SCT_obj <- AddMetaData(SCT_obj,
                       metadata = NPC_obj$Identity, 
                       col.name = "Identity")
UMAPPlot(SCT_obj, group.by = "Identity", label = T) + NoLegend()
```


```{r Save object}
saveRDS(SCT_obj, file = "Objects/SCT_obj.rds")
sessionInfo()
```
